---
output:
  github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
# opencage

<!-- badges: start -->

[![CRAN Status](https://www.r-pkg.org/badges/version/opencage)](https://cran.r-project.org/package=opencage)
[![CRAN Checks](https://cranchecks.info/badges/worst/opencage)](https://cran.r-project.org/web/checks/check_results_opencage.html)
[![CRAN Downloads per Month](https://cranlogs.r-pkg.org/badges/opencage)](https://cran.r-project.org/package=opencage)
[![R-CMD-check](https://github.com/ropensci/opencage/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/opencage/actions?query=workflow%3AR-CMD-check)
[![codecov.io](https://codecov.io/github/ropensci/opencage/coverage.svg?branch=master)](https://codecov.io/github/ropensci/opencage?branch=master)
[![rOpenSci Peer-Review](https://badges.ropensci.org/36_status.svg)](https://github.com/ropensci/software-review/issues/36)
[![License](https://img.shields.io/cran/l/opencage)](https://opensource.org/licenses/gpl-license)

<!-- badges: end -->

Geocode with the [OpenCage](https://opencagedata.com) API, either from place name to longitude and latitude (forward geocoding) or from longitude and latitude to the name and address of the location (reverse geocoding). 

## Installation

Install the package with:

```{r eval = FALSE}
install.packages("opencage")
```

Or install the development version using [remotes](https://remotes.r-lib.org) with:

```{r, eval = FALSE}
remotes::install_github("ropensci/opencage")

```

## Quickstart

For the best experience, we recommend that you read through the "Introduction to opencage" vignette (`vignette("opencage")`), but if you are in a hurry:

1. Register at [opencagedata.com/users/sign_up](https://opencagedata.com/users/sign_up).
2. Generate an API key at the [OpenCage dashboard](https://opencagedata.com/dashboard#api-keys).
3. Save your API key as an [environment variable](https://rstats.wtf/r-startup.html#renviron) like `OPENCAGE_KEY=yourkey` in `.Renviron`. 
See `help(oc_config)` for alternative ways to set your OpenCage API key.

Now you are ready to turn place names into latitude and longitude coordinates:

```{r forward}
library(opencage)
oc_forward_df(placename = "Sarzeau")
```

Or turn a set of coordinates into the name and address of the location:

```{r reverse}
oc_reverse_df(latitude = 51.5034070, longitude = -0.1275920)
```

But remember, the vignettes are really great! We have:

- "Introduction to opencage" `vignette("opencage")`
- "Customise your query" `vignette("customise_query")`
- "Output options" `vignette("output_options")`

## About OpenCage

The [OpenCage](https://opencagedata.com) API supports forward and reverse geocoding. 
Sources of OpenCage are open geospatial data including 
[OpenStreetMap](https://www.openstreetmap.org), 
[DataScienceToolkit](https://github.com/petewarden/dstk), 
[GeoPlanet](https://en.wikipedia.org/wiki/GeoPlanet), 
[Natural Earth Data](https://www.naturalearthdata.com), 
[libpostal](https://github.com/openvenues/libpostal), 
[GeoNames](https://www.geonames.org), and 
[Flickr's shapefiles](https://code.flickr.net/2009/05/21/flickr-shapefiles-public-dataset-10/) plus a whole lot more besides. 
Refer to the current full [list of credits](https://opencagedata.com/credits).

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/opencage/issues).
* License: GPL >= 2
* Get citation information for `opencage` in R doing `citation(package = 'opencage')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
