---
title: "opencage R package"
author: "Maëlle Salmon"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---
opencage
=============

[![Build Status](https://travis-ci.org/masalmon/opencage.svg?branch=master)](https://travis-ci.org/masalmon/opencage)

# Installation

To install the package, you will need the devtools package.

```{r, eval = FALSE}
library("devtools")
install_github("masalmon/opencage")

```

To use the package, you will also need an API key. For this register at https://geocoder.opencagedata.com/pricing. The free API key provides up to 2,500 calls a day. It is recommended you save your API key as an environment variable. See https://stat545-ubc.github.io/bit003_api-key-env-var.html

# Geocoding

The opencage API supports forward and reverse geocoding. Below are two easy examples. For more information about the query parameters, see the package documentation.

## Forward geocoding

Forward geocoding is from placename to latitude and longitude tuplet(s).

```{r}
library("opencage")
opencage_forward(placename = "Sarzeau", key = Sys.getenv("OPENCAGE_KEY"))
```

## Reverse geocoding

Reverse geocoding is from latitude and longitude to placename(s).

```{r}
opencage_reverse(latitude = 0, longitude = 0, 
                 key = Sys.getenv("OPENCAGE_KEY"),
                 limit = 2)
```
