---
title: "shtr-pls_address-abbreviations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shtr-pls_address-abbreviations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(opencage)
```

Since 2017 OpenCage have been providing [abbreviated addresses](https://blog.opencagedata.com/post/160294347883/shrtr-pls) via their API. This might be particularly useful when displaying addresses in popups on maps.

All forward/reverse geocoding functions in `{opencage}` include `abbrv = FALSE` by default

```{r include=FALSE}
library("tidyverse")
```

```{r}
library("tidyverse")
oc_reverse(44.4283569,26.0889539) %>%
  unnest(cols = data) %>%
  pull(oc_formatted)
```

OpenCage includes many common address abbreviations that may be combined with non-native language address requests via the `abbrv` and `language` arguments:

```{r}
oc_reverse(44.4283569,26.0889539,
           abbrv = TRUE,
           language = "zh") %>%
  unnest(cols = data) %>%
  pull(oc_formatted)
```
