---
title: "opencage-gdpr-compliance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{opencage-gdpr-compliance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(opencage)
```

## Privacy

All geocoding functions have a parameter `no_record`. It is `FALSE` by default. 

* When `no_record` is `FALSE` a log of the query is made by OpenCage. These logs are used for debugging and in order to improve the service. [According to OpenCage](https://opencagedata.com/faq#legal), all logs are automatically deleted after six months. 

* When `no_record` is `TRUE`, OpenCage still records that a request was made (e.g. to see whether you exceeded your quota), but not the specific content of your query. Please set `no_record` to `TRUE` if you have concerns about privacy and don't want OpenCage to have a record of your query. More information about privacy can be found on OpenCage's [GDPR page](https://opencagedata.com/gdpr).
